State of the Practice of Lattice Boltzmann Method Software Development

### 2021-07-27 StateOfPractice/Peter-Notes/Report/Report.tex
updated LBM report section 6.1

\noindent\textbf{NUMBER OF PAGES:} 120

@@

The software packages were examined for the presence of artifacts, which were then categorized by frequency. Below we have grouped them into common, less common, and rare artifacts. Common artifacts were found in 16 to 23 ($>$70\%) of the software packages. Less common artifacts were found in 8 to 15 (35-70\%) of the software packages. Rare artifacts were found in 1 to 7 ($<$35\%) of the software packages.

\subsubsection{Common Artifacts}
The following artifacts were commonly found in the 23 software packages that were tested. All of the top four AHP ranked packages, ESPREsSo, Ludwig, OpenLB, and Palabos, have each of these artifacts, except only three of them have a requirements specification or theory notes. Palabos is the only one of these four packages that does not have an artifact from this category.

\begin{multicols}{2}	
\begin{itemize}
	\begin{singlespace}
		\item Authors/Developers List
		\item Bug Tracker
		\item Dependency Notes 
		\item Installation Guide/Instructions 
		\item License
		\item List of Related Articles/Publications 
		\item Makefile / Build File 
		\item README File 
		\item Requirements Specification / Theory Notes
		\item Tutorial
	\end{singlespace}
\end{itemize}
\end{multicols}

These common artifacts contribute to the quality of the software in the following ways. A list of authors and developers helps potential users and contributors contact project members to answer questions affecting many software qualities. A bug tracker helps with organizing improvements to the software. Dependency notes help users install the software, as does an installation guide. Makefiles or other automated build files decrease human error in the installation process. Licenses promote usage of the software. Requirements specifications, linked theory notes, and related articles and publications help make the software more understandable, decrease ambiguity, and help with verifying its correctness. README files also help with understandability. The tutorials help users become familiar with using the software.

\subsubsection{Less Common Artifacts}\label{lesscommon}
The following artifacts were less commonly found in the 23 software packages that were tested. The top four AHP ranked packages have most of these artifacts.
At the time of data collection, only one (Palabos) of the four packages did not have a user manual or guide, but there was a broken link on the package website indicating that such an artifact might exist. This broken link was later fixed, but this is not reflected in our data because it was not present at the time of data collection. Despite the broken link, Palabos does have a detailed and informative website. Another one (Ludwig) of the top four packages does not appear to have publicly visible design documentation. A third package (OpenLB) from the list does not appear to use a version control system. It is possible that such a system is used by the package since its website notes package version numbers, but the artifacts do not explicitly state the use of such a system.

	\begin{multicols}{2}	
		\begin{itemize}
			\begin{singlespace}
			\item Change Log / Release Notes
			\item Design Documentation
			\item Functional Specification/Notes	
			\item Performance Information/Notes
			\item Test Plan/Report/Script/Data/Cases
			\item User Manual/Guide
			\item Version Control
		\end{singlespace}
		\end{itemize}
	\end{multicols}

These artifacts also contribute to software quality. A change log or release notes improve traceability of the software. Design documentation helps with maintaining, modifying, and reusing the software. Version control also helps to improve these qualities, as well as with traceability. Functional specifications and notes clarify the software, contributing to usability and understandability. A user manual also helps with those qualities and with installability, and correctness and verificability. Performance notes suggest that performance was considered when developing the software. Test plans, scripts, and cases, help verify correctness.

\subsubsection{Rare Artifacts}
The following artifacts were rarely found in the 23 software packages that were assessed. It is not common for the top four AHP ranked packages to have many of these artifacts. None of the top four packages have any explicit API documentation. Three of these packages (ESPREsSo, Ludwig, Palabos) have information on contributing to the project. Two of them (OpenLB, Palabos) have a FAQ section or forum. One (OpenLB) has verification and validation notes, and a video guide of the software.

	\begin{multicols}{2}	
		\begin{itemize}
			\begin{singlespace}
				\item API Documentation
				\item Developer/Contributor Manual/Guide
				\item FAQ / Forum
				\item Verification and Validation Plan/Notes
				\item Video Guide (including YouTube)
			\end{singlespace}
		\end{itemize}
	\end{multicols}

Although these artifacts were rarely found in our set of LBM software, they also contribute to software quality. API documentation helps with reusing the software. Developer and contributor manuals and guides help with maintainability, visibility and transparency. FAQs and forums improve usability of software. Verification and validation notes can be used to help check if a system meets specifications. Video guides can contribute to many software qualities, depending on the content of the video.

>>>>

\noindent\textbf{NUMBER OF PAGES:} 121

@@

The software packages were examined for the presence of artifacts, which were then categorized by frequency. We have grouped them into common, less common, and rare artifacts in Table \ref{artifactspresent}. Common artifacts were found in 16 to 23 ($>$70\%) of the software packages. Less common artifacts were found in 8 to 15 (35-70\%) of the software packages. Rare artifacts were found in 1 to 7 ($<$35\%) of the software packages.

\begin{onehalfspace}
	\begin{center}
		\begin{tabular}{ p{8 cm} }
			\hline
			Common\\
			\hline
			Authors / Developers List\\
			Bug Tracker\\
			Dependency Notes\\
			Installation Guide / Instructions\\
			License\\
			List of Related Articles / Publications\\
			Makefile / Build File\\
			README File\\
			Requirements Specification / Theory Notes\\
			Tutorial\\
			\hline
			Less Common\\
			\hline
			Change Log / Release Notes\\
			Design Documentation\\
			Functional Specification / Notes\\
			Performance Information / Notes\\
			Test Plan / Report / Script / Data / Cases\\
			User Manual/Guide\\
			Version Control\\
			\hline
			Rare\\
			\hline
			API Documentation\\
			Developer / Contributor Manual / Guide\\
			FAQ / Forum\\
			Verification and Validation Plan / Notes\\
			Video Guide (including YouTube)\\
			\hline
		\end{tabular}
		\captionof{table}{Artifacts Present}\label{artifactspresent}
	\end{center}
\end{onehalfspace}

\subsubsection{Common Artifacts}
All of the top four AHP ranked packages, ESPREsSo, Ludwig, OpenLB, and Palabos, have each of the commonly found artifacts, except only three of them have a requirements specification or theory notes. Palabos is the only one of these four packages that does not have an artifact from this category.

The common artifacts contribute to the quality of the software in the following ways. A list of authors and developers helps potential users and contributors contact project members to answer questions affecting many software qualities. A bug tracker helps with organizing improvements to the software. Dependency notes help users install the software, as does an installation guide. Makefiles or other automated build files decrease human error in the installation process. Licenses promote usage of the software. Requirements specifications, linked theory notes, and related articles and publications help make the software more understandable, decrease ambiguity, and help with verifying its correctness. README files also help with understandability. The tutorials help users become familiar with using the software.

\subsubsection{Less Common Artifacts}\label{lesscommon}
The top four AHP ranked packages have most of the less common artifacts.
At the time of data collection, only one (Palabos) of the four packages did not have a user manual or guide, but there was a broken link on the package website indicating that such an artifact might exist. This broken link was later fixed, but this is not reflected in our data because it was not present at the time of data collection. Despite the broken link, Palabos does have a detailed and informative website. Another one (Ludwig) of the top four packages does not appear to have publicly visible design documentation. A third package (OpenLB) from the list does not appear to use a version control system. It is possible that such a system is used by the package since its website notes package version numbers, but the artifacts do not explicitly state the use of such a system.

The less common artifacts also contribute to software quality. A change log or release notes improve traceability of the software. Design documentation helps with maintaining, modifying, and reusing the software. Version control also helps to improve these qualities, as well as with traceability. Functional specifications and notes clarify the software, contributing to usability and understandability. A user manual also helps with those qualities and with installability, and correctness and verificability. Performance notes suggest that performance was considered when developing the software. Test plans, scripts, and cases, help verify correctness.

\subsubsection{Rare Artifacts}
It is not common for the top four AHP ranked packages to have many of the rare artifacts. None of the top four packages have any explicit API documentation. Three of these packages (ESPREsSo, Ludwig, Palabos) have information on contributing to the project. Two of them (OpenLB, Palabos) have a FAQ section or forum. One (OpenLB) has verification and validation notes, and a video guide of the software.

Although the artifacts were rarely found in our set of LBM software, they also contribute to software quality. API documentation helps with reusing the software. Developer and contributor manuals and guides help with maintainability, visibility and transparency. FAQs and forums improve usability of software. Verification and validation notes can be used to help check if a system meets specifications. Video guides can contribute to many software qualities, depending on the content of the video.
